Architectures and Open pNets

### 2018-10-20 2018-Arch-pNets/arch-pNets.tex
Arch-pNets paper: Added an sketch of the encoding of maximal progress

>>>>

\noteSBin{In order to encode the maximal progress priority model, one
  has to introduce an additional Boolean variable, for each port (for
  which we have introduced one in $\nopri[A, \partition]$), such that
  $q \goesto{p(b_p, \true)} q'$ iff $\exists q'': q \goesto{p(\true)}
  q''$ in $\nopri[A, \partition]$.  Intuitively, this variable
  indicates whether \emph{there is a possibility to fire $p$ from the
    same state}.  Then, in the SV guard, we have to check whether
  \emph{all ports in $c_p(\tau(x))$ can be fired} (see
  \app{transformations}).  If so, then $p$ must be fired, \ie
  $p(\false)$ must be blocked.  This is pretty much straightforward,
  but care must be taken when doing this in the general case, since
  causal interaction trees can get pretty tricky due to $\oplus$ (see
  \app{trees}).}
%****************************************************************
%****************************************************************
